A bit _introduction_ here.

# Start with a cool section

You can use traditional **Markdown** syntax, such as [links](http://yihui.name/knitr) and `code`.

# Followed by another section

Of course you can write lists:

- apple
- pear
- banana

Or ordered lists:

1. items
1. will
1. be
1. ordered
    - nested
    - items

# More sections

## Hi

Hi, try to find me on <http://www.github.com>, luke!

## Hello quotes

hello hello, try \doublequotes{to double quote me}, with italic also works?

Suspence \omissis{} *\doublequotes{yes you can!}*.

But I can \citquotes{cite} someone? Sure you can!

Consider that the quotes in `.md` are trivial to do: simply type, "try it yourself", and 'again' if you do not trust!

Note that if you udefine the `csquotes` variabile in the `.pandoc` configuration file, the \citquotes{citation quotes} will be the default ones.

However you can type what quotes you want with \LaTeX ! ;)

Now is time for imagination. See section \ref{sec:pictures} (only `hyperref` works).

## How to define, theorize something?

\begin{definizione}[The surprise]This is a surprise!\end{definizione}

So we can say:
\begin{teorema}[The end of the world]MarkDown, Knitr, \LaTeX, and Pandoc are the end of the world. A new world is coming!\end{teorema}

# Okay, some R code

```{r linear-model}
fit = lm(dist ~ speed, data = cars)
b = coef(fit)  # coefficients
summary(fit)
```

The code will be highlighted in all output formats.

# And some pictures
\label{sec:pictures}
```{r lm-vis, fig.cap='Regression diagnostics'}
par(mfrow = c(2, 2), pch = 20, mar = c(4, 4, 2, .1), bg = 'white')
plot(fit)
```

But I have a old image that i want to load! Sure you can do, with \LaTeX directly into MarkDown!

\begin{figure}
\includegraphics{gallery}
\caption[A gallery]{\label{fig:gallery}A long caption for my gallery image.}
\end{figure}

Reference the \cref{fig:gallery}, \vref{fig:gallery}, immagine \ref{fig:gallery}.

And if I only want to use MarkDown?

![Another gallery\label{fig:lorem}](lorem)

Wonderful! It detects also the `images` folder that have ben set to be the _home_ of the images!

I can also references the previous `.md` image: \cref{fig:lorem}, \vref{fig:lorem}, \ref{fig:lorem}.


```{r example-plot, fig.cap = "A simple example plot\\label{fig:example-plot}"}
plot(1:10, 1:10)
```

Prova \cref{fig:example-plot}, \vref{fig:example-plot}, \ref{fig:example-plot}

```{r test-plot}
plot(1)         # high-level plot
abline(0, 1)    # low-level change
plot(rnorm(10)) # high-level plot
## many low-level changes in a loop (a single R expression)
for(i in 1:10) {
    abline(v = i, lty = 2)
}
```

Prova \ref{test-plot}

Prova \ref{fig:test-plot}

# A little bit math

Our regression equation is $Y=`r b[1]`+`r b[2]`x$, and the model is:

$$ Y = \beta_0 + \beta_1 x + \epsilon $$

# References

## Hyperref ?

## Vref ?

## Cref ?

# Pandoc extension: definition lists

Programmer
:   A programmer is the one who turns coffee into code.
LaTeX
:   A simple tool which is nothing but a couple of backslashes.

# Pandoc extension: examples

We have some examples.

(@) Think what is `0.3 + 0.4 - 0.7`. Zero. Easy.
(@weird) Now think what is `0.3 - 0.7 + 0.4`. Still zero?

People are often surprised by (@weird).

# Pandoc extension: tables

A table here.

Table:  Demonstration of simple table syntax.

  Right     Left     Center     Default
-------     ------ ----------   -------
     12     12        12            12
    123     123       123          123
      1     1          1             1

## Tables with `xtable`

A table generated with `xtable` package.

```{r example_table, echo=FALSE, results="asis"}
library(xtable)
suppressPackageStartupMessages(library(rattle))
set.seed(42)
obs <- sample(1:nrow(weatherAUS), 20)
vars <- 2:5
print(xtable(weatherAUS[obs, vars]), comment = FALSE)
```

## Tables with `kable`

### Simple `kable`

```{r, echo=FALSE, results="asis"}
kable(head(iris), format = "latex")
```

### With `booktabs` package

With `booktabs` option \omissis{}

```{r, echo=FALSE, results="asis"}
kable(head(mtcars[1:8]), format = "latex", booktabs = TRUE)
```

\omissis{} or without it!

```{r, echo=FALSE, results="asis"}
kable(head(mtcars[1:8]), format = "latex", booktabs = FALSE)
```

### With `longtables` package

```{r, longtablet, echo=FALSE, results="asis"}
kable(matrix(1000, ncol = 5), format = "latex", digits = 2, longtable = TRUE)
```

Prova riferimento a <longtablet>.

# Pandoc extension: footnotes

We can also write footnotes[^1].

[^1]: hi, I'm a footnote

Or write some inline footnotes^[as you can see here].

# Pandoc extension: citations

We compile the R Markdown file to Markdown through **knitr** [@xie2013] in R [@rbase]. For more about @xie2013, see <http://yihui.name/knitr>.

Dai su!

\appendix

```{r appendix-a, child="appendix-a.Rmd", eval=TRUE}

```

```{r appendix-b, child="appendix-b.Rmd", eval=TRUE}

```

\phantomsection
\pdfbookmark{\refname}{\bibname}
\section*{\bibname}
